---
title: "Data Structures in Fate Explorer"
author: "Dr. Jan Seifert"
date: "14 6 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Enumerations

Enumerations are realised as named atomic vectors.

```{r echo=FALSE}
source("./src/weapon.R")
#.WeaponType    <- c(Weaponless = 0L, Melee = 1L, Ranged = 2L)
print(.WeaponType)
#.CombatActions <- c(Attack = 1L, Parry = 2L, Dodge = 3L)
print(.CombatActions)
#.SuccessLevels <- c(Fumble = 1L, Fail = 2L, Success = 3L, Critical = 4L)
print(.SuccessLevels)
```



CombatTechniques


# Basic Tables {.tabset}

## Abilities

`GetAbilities()`

```{r echo=FALSE}
ab <- structure(list(attrID = c("ATTR_1", "ATTR_2", "ATTR_3", "ATTR_4", 
"ATTR_5", "ATTR_6", "ATTR_7", "ATTR_8"), shortname = c("MU", 
"KL", "IN", "CH", "FF", "GE", "KO", "KK"), name = c("Mut", "Klugheit", 
"Intuition", "Charisma", "Fingerfertigkeit", "Gewandheit", "Konstitution", 
"Körperkraft")), class = "data.frame", row.names = c(NA, 8L))
ab
```

* Type: <`r class(ab)`>
* Identifiers are stored in first column `attrID` (language independent)
* Available in German and English
* Loaded from "attributes_[lang].json"



## Skills

`GetSkills()`

```{r echo=FALSE}
sk <- structure(list(attrID = c("TAL_1", "TAL_2", "TAL_3", "TAL_4", 
"TAL_5", "TAL_6"), name = c("Fliegen", "Gaukeleien", "Klettern", 
"Körperbeherrschung", "Kraftakt", "Reiten"), class = c("Körpertalente", 
"Körpertalente", "Körpertalente", "Körpertalente", "Körpertalente", 
"Körpertalente"), classID = c(1L, 1L, 1L, 1L, 1L, 1L), ab1 = c("ATTR_1", 
"ATTR_1", "ATTR_1", "ATTR_6", "ATTR_7", "ATTR_4"), ab2 = c("ATTR_3", 
"ATTR_4", "ATTR_6", "ATTR_6", "ATTR_8", "ATTR_6"), ab3 = c("ATTR_6", 
"ATTR_5", "ATTR_8", "ATTR_7", "ATTR_8", "ATTR_8")), row.names = c(NA, 
6L), class = "data.frame")
sk
```

* Type: <`r class(sk)`>
* Identifiers are stored in first column `attrID` (language independent)
* Available only in German at the moment
* Loaded from "skills_[lang].json"


## Weapons

`GetWeapons()`

```{r echo=FALSE}
wp <- structure(list(name = c("Basiliskenzunge", "Dolch", "Drachenzahn", 
"Linkhand", "Messer", "SchwererDolch"), combattech = c("Dolche", 
"Dolche", "Dolche", "Dolche", "Dolche", "Dolche"), primaryattr = c("GE", 
"GE", "GE", "GE", "GE", "GE"), threshold = c(14L, 14L, 14L, 14L, 
14L, 14L), damage = c("1W6", "1W6", "1W6", "1W6", "1W6", "1W6"
), bonus = c(2L, 1L, 2L, 1L, 1L, 2L), at = c(0L, 0L, 0L, 0L, 
0L, 0L), pa = c(-1L, 0L, -1L, 0L, -2L, -1L), range = c("kurz", 
"kurz", "kurz", "kurz", "kurz", "kurz"), weight = c("0,5Stn", 
"0,5Stn", "0,75Stn", "0,75Stn", "0,25Stn", "0,75Stn"), price = c(50, 
45, 70, 90, 10, 60), sf = c(12L, 12L, 12L, 12L, 12L, 12L), primeattrID = c("ATTR_6", 
"ATTR_6", "ATTR_6", "ATTR_6", "ATTR_6", "ATTR_6"), combattechID = c("CT_3", 
"CT_3", "CT_3", "CT_3", "CT_3", "CT_3"), improvised = c(FALSE, 
FALSE, FALSE, FALSE, FALSE, FALSE), url = c("index.php/basiliskenzunge.html", 
"index.php/dolch.html", "index.php/drachenzahn.html", "index.php/linkhand.html", 
"index.php/messer.html", "index.php/schwerer-dolch.html"), clsrng = c(TRUE, 
TRUE, TRUE, TRUE, TRUE, TRUE), armed = c(TRUE, TRUE, TRUE, TRUE, 
TRUE, TRUE)), row.names = c(NA, 6L), class = "data.frame")
wp
```

* Type: <`r class(wp)`>
* Identifiers (at this point) are stored in the "name" column 
* Available in German
* Loaded from "weapon-list.json"
* Columns
  * `$name` (language dependent)
  * `$combattech` Label of combat technique (language dependent)
  * `$combattechID` Combat technique (ID)
  * `$primaryattr` Label of primary weapons attribute(s) (language dependent)
  * `$primeattrID` Primary weapons attribute(s) (ID)
  * `$threshold`
  * `$damage` 
  * `$bonus` 
  * `$at` 
  * `$pa` 
  * `$range` label for range (language dependent)
  * `$weight` (language dependent)
  * `$price` 
  * `$sf` sheer factor (German: Bruchfaktor)
  * `$improvised` (`TRUE`/`FALSE`)
  * `$clsrng` data set represents weapon values for close or ranged combat (`TRUE`/`FALSE`)
  * `$armed` is armed combat? (`TRUE`/`FALSE`)
  * `$url` (`TRUE`/`FALSE`)


`GetWeapons("Waqqif")`

```{r echo=FALSE}
# dput(GetWeapons("Waqqif"))
wp <- list(name = "Waqqif", technik = "Dolche", leiteigenschaft = "GE", 
    schwelle = 14L, grundschaden = "1W6", bonus = 2L, at = 0L, 
    pa = -1L, rw = "kurz", gewicht = "0,5Stn", preis = 60, bf = 12L, 
    primeattrID = "ATTR_6", combattechID = "CT_3", improvised = FALSE, 
    url = "index.php/waqqif.html")
wp
```

* Type: <`r class(wp)`> (list)


# Character {.tabset}

## Name

* Type: `character(1)`


## Abilities

```{r echo=FALSE}
ab <- structure(list(ATTR_1 = 12L, ATTR_2 = 11L, ATTR_3 = 13L, ATTR_4 = 14L, 
    ATTR_5 = 13L, ATTR_6 = 16L, ATTR_7 = 11L, ATTR_8 = 11L), class = "data.frame", row.names = c(NA, -1L))
ab
```

* Type: <`r class(ab)`>
* Identifiers are stored in the names (`names(Character$Attr)`)



## Weapons

```{r echo=FALSE}
wp <- structure(c("Waffenlos", "16", "10", "1", "0", "Nachtwind", "13", 
"8", "1", "4", "Waqqif", "16", "9", "1", "2"), .Dim = c(5L, 3L
), .Dimnames = list(c("Name", "AT", "PA", "DamageDice", "DamageMod"
), c("Waffenlos", "Nachtwind", "Waqqif")))
wp
```

* Type: <`r class(wp)`>
* Idenfitfiers are German weapon names  stored in the column names and first row
  * Access id with `Character$Weapons[1,]`
  * Access id with `names(Character$Weapons)`

## Skills

```{r echo=FALSE}
sk <- structure(list(attrID = c("TAL_1", "TAL_2", "TAL_3", "TAL_4", 
"TAL_5", "TAL_6", "TAL_7", "TAL_8", "TAL_9", "TAL_10", "TAL_11", 
"TAL_12", "TAL_13", "TAL_14", "TAL_15", "TAL_16", "TAL_17", "TAL_18", 
"TAL_19", "TAL_20", "TAL_21", "TAL_22", "TAL_23", "TAL_24", "TAL_25", 
"TAL_26", "TAL_27", "TAL_28", "TAL_29", "TAL_30", "TAL_31", "TAL_32", 
"TAL_33", "TAL_34", "TAL_35", "TAL_36", "TAL_37", "TAL_38", "TAL_39", 
"TAL_40", "TAL_41", "TAL_42", "TAL_43", "TAL_44", "TAL_45", "TAL_46", 
"TAL_47", "TAL_48", "TAL_49", "TAL_50", "TAL_51", "TAL_52", "TAL_53", 
"TAL_54", "TAL_55", "TAL_56", "TAL_57", "TAL_58", "TAL_59"), 
    name = c("Fliegen", "Gaukeleien", "Klettern", "Körperbeherrschung", 
    "Kraftakt", "Reiten", "Schwimmen", "Selbstbeherrschung", 
    "Singen", "Sinnesschärfe", "Tanzen", "Taschendiebstahl", 
    "Verbergen", "Zechen", "Bekehren & Überzeugen", "Betören", 
    "Einschüchtern", "Etikette", "Gassenwissen", "Menschenkenntnis", 
    "Überreden", "Verkleiden", "Willenskraft", "Fährtensuchen", 
    "Fesseln", "Fischen & Angeln", "Orientierung", "Pflanzenkunde", 
    "Tierkunde", "Wildnisleben", "Brett- & Glückspiel", "Geographie", 
    "Geschichtswissen", "Götter & Kulte", "Kriegskunst", "Magiekunde", 
    "Mechanik", "Rechnen", "Rechtskunde", "Sagen & Legenden", 
    "Sphärenkunde", "Sternkunde", "Alchimie", "Boote & Schiffe", 
    "Fahrzeuge", "Handel", "Heilkunde Gift", "Heilkunde Krankheiten", 
    "Heilkunde Seele", "Heilkunde Wunden", "Holzbearbeitung", 
    "Lebensmittelbearbeitung", "Lederbearbeitung", "Malen & Zeichnen", 
    "Metallbearbeitung", "Musizieren", "Schlösserknacken", "Steinbearbeitung", 
    "Stoffbearbeitung"), class = c("Körpertalente", "Körpertalente", 
    "Körpertalente", "Körpertalente", "Körpertalente", "Körpertalente", 
    "Körpertalente", "Körpertalente", "Körpertalente", "Körpertalente", 
    "Körpertalente", "Körpertalente", "Körpertalente", "Körpertalente", 
    "Gesellschaftstalente", "Gesellschaftstalente", "Gesellschaftstalente", 
    "Gesellschaftstalente", "Gesellschaftstalente", "Gesellschaftstalente", 
    "Gesellschaftstalente", "Gesellschaftstalente", "Gesellschaftstalente", 
    "Naturtalente", "Naturtalente", "Naturtalente", "Naturtalente", 
    "Naturtalente", "Naturtalente", "Naturtalente", "Wissenstalente", 
    "Wissenstalente", "Wissenstalente", "Wissenstalente", "Wissenstalente", 
    "Wissenstalente", "Wissenstalente", "Wissenstalente", "Wissenstalente", 
    "Wissenstalente", "Wissenstalente", "Wissenstalente", "Handwerkstalente", 
    "Handwerkstalente", "Handwerkstalente", "Handwerkstalente", 
    "Handwerkstalente", "Handwerkstalente", "Handwerkstalente", 
    "Handwerkstalente", "Handwerkstalente", "Handwerkstalente", 
    "Handwerkstalente", "Handwerkstalente", "Handwerkstalente", 
    "Handwerkstalente", "Handwerkstalente", "Handwerkstalente", 
    "Handwerkstalente"), classID = c(1L, 1L, 1L, 1L, 1L, 1L, 
    1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 
    2L, 2L, 3L, 3L, 3L, 3L, 3L, 3L, 3L, 4L, 4L, 4L, 4L, 4L, 4L, 
    4L, 4L, 4L, 4L, 4L, 4L, 5L, 5L, 5L, 5L, 5L, 5L, 5L, 5L, 5L, 
    5L, 5L, 5L, 5L, 5L, 5L, 5L, 5L), ab1 = c("ATTR_1", "ATTR_1", 
    "ATTR_1", "ATTR_6", "ATTR_7", "ATTR_4", "ATTR_6", "ATTR_1", 
    "ATTR_2", "ATTR_2", "ATTR_2", "ATTR_1", "ATTR_1", "ATTR_2", 
    "ATTR_1", "ATTR_1", "ATTR_1", "ATTR_1", "ATTR_2", "ATTR_2", 
    "ATTR_1", "ATTR_3", "ATTR_1", "ATTR_1", "ATTR_2", "ATTR_5", 
    "ATTR_2", "ATTR_2", "ATTR_1", "ATTR_1", "ATTR_2", "ATTR_2", 
    "ATTR_2", "ATTR_2", "ATTR_1", "ATTR_2", "ATTR_2", "ATTR_2", 
    "ATTR_2", "ATTR_2", "ATTR_2", "ATTR_2", "ATTR_1", "ATTR_5", 
    "ATTR_4", "ATTR_2", "ATTR_1", "ATTR_1", "ATTR_3", "ATTR_2", 
    "ATTR_5", "ATTR_3", "ATTR_5", "ATTR_3", "ATTR_5", "ATTR_4", 
    "ATTR_3", "ATTR_5", "ATTR_2"), ab2 = c("ATTR_3", "ATTR_4", 
    "ATTR_6", "ATTR_6", "ATTR_8", "ATTR_6", "ATTR_7", "ATTR_1", 
    "ATTR_4", "ATTR_3", "ATTR_4", "ATTR_5", "ATTR_3", "ATTR_7", 
    "ATTR_2", "ATTR_4", "ATTR_3", "ATTR_3", "ATTR_3", "ATTR_3", 
    "ATTR_3", "ATTR_4", "ATTR_3", "ATTR_3", "ATTR_5", "ATTR_6", 
    "ATTR_3", "ATTR_5", "ATTR_1", "ATTR_6", "ATTR_2", "ATTR_2", 
    "ATTR_2", "ATTR_2", "ATTR_2", "ATTR_2", "ATTR_2", "ATTR_2", 
    "ATTR_2", "ATTR_2", "ATTR_2", "ATTR_2", "ATTR_2", "ATTR_6", 
    "ATTR_5", "ATTR_3", "ATTR_2", "ATTR_3", "ATTR_4", "ATTR_5", 
    "ATTR_6", "ATTR_5", "ATTR_6", "ATTR_5", "ATTR_7", "ATTR_5", 
    "ATTR_5", "ATTR_5", "ATTR_5"), ab3 = c("ATTR_6", "ATTR_5", 
    "ATTR_8", "ATTR_7", "ATTR_8", "ATTR_8", "ATTR_8", "ATTR_7", 
    "ATTR_7", "ATTR_3", "ATTR_6", "ATTR_6", "ATTR_6", "ATTR_8", 
    "ATTR_4", "ATTR_4", "ATTR_4", "ATTR_4", "ATTR_4", "ATTR_4", 
    "ATTR_4", "ATTR_6", "ATTR_4", "ATTR_6", "ATTR_8", "ATTR_7", 
    "ATTR_3", "ATTR_7", "ATTR_4", "ATTR_7", "ATTR_3", "ATTR_3", 
    "ATTR_3", "ATTR_3", "ATTR_3", "ATTR_3", "ATTR_5", "ATTR_3", 
    "ATTR_3", "ATTR_3", "ATTR_3", "ATTR_3", "ATTR_5", "ATTR_8", 
    "ATTR_7", "ATTR_4", "ATTR_3", "ATTR_7", "ATTR_7", "ATTR_5", 
    "ATTR_8", "ATTR_5", "ATTR_7", "ATTR_5", "ATTR_8", "ATTR_7", 
    "ATTR_5", "ATTR_8", "ATTR_5"), value = c(0, 0, 10, 11, 0, 
    5, 0, 7, 0, 10, 3, 4, 10, 0, 0, 0, 0, 7, 8, 8, 10, 10, 8, 
    1, 0, 0, 3, 0, 0, 4, 1, 4, 3, 4, 0, 0, 2, 4, 3, 3, 0, 0, 
    2, 3, 2, 8, 4, 0, 0, 4, 0, 0, 3, 3, 0, 0, 7, 0, 12)), row.names = c(NA, 
59L), class = "data.frame")
head(sk)
```

* Type: <`r class(sk)`>
* Skill idenfitfiers are stored in the first column `attrID`.
  * Access id with `Character$Skill[["attrID"]]`
* Ability identifiers are coded as `r paste("ATTR_", 1:8)`
* Skill class is a numeric identifier